### 2019-12-09 ch0_frontmatter.tex
fixes to front matter

\hypersetup{%
	pdftitle = {Modelling single cell dynamics with trajectories and gene regulatory networks},
	pdfsubject = {A subject},
	pdfkeywords = {import keywords},
	pdfauthor = {Robrecht Cannoodt},
	pdfcreator = {\LaTeX},
}

@@

	\includegraphics[width=\linewidth]{fig/logos/mashup}
%	\includegraphics[height=.7cm]{fig/logos/icon_UGent_WE_EN_RGB_color}\hfill
%	\includegraphics[height=1cm]{fig/logos/vib_rf_inflammation_research_rgb_pos} \hfill
%	\includegraphics[height=.8cm]{fig/logos/dambi_logo} \hfill
%	\includegraphics[height=.7cm]{fig/logos/cmgg_myshort} \hfill
%	\includegraphics[height=.7cm]{fig/logos/FWO_Logo_KleurCMYK} 
	\vspace{1cm}

@@

Finally, I reflect on current challenges within the field, by providing guidelines for how to self-assess trajectory inference methods (Chapter~\ref{chap:selfassessment}) and, more generally, how to perform large-scale benchmarking experiments of computational methods (Chapter~\ref{chap:guidelines}).

@@

Ik reflecteer op huidige uitdagingen binnen het veld, door richtlijnen aan te bieden aan ontwikkelaars voor het evalueren van hun trajectvoorspellende methoden (Hoofdstuk~\ref{chap:selfassessment}), en meer algemeen over hoe grootschalige benchmarkingsexperimenten van computationele methoden kunnen worden uitgevoerd (Hoofdstuk~\ref{chap:guidelines}).

>>>>

\hypersetup{%
	pdftitle = {Modelling single-cell dynamics with trajectories and gene regulatory networks},
	pdfsubject = {A subject},
	pdfkeywords = {import keywords},
	pdfauthor = {Robrecht Cannoodt},
	pdfcreator = {\LaTeX},
}

@@

	\includegraphics[width=\linewidth]{fig/logos/mashup}
	\vspace{1cm}

@@

Finally, I reflect on current challenges within the field, by providing guidelines on how to perform large-scale benchmarking experiments of computational methods (Chapter~\ref{chap:guidelines}).

@@

Ik reflecteer op huidige uitdagingen binnen het veld, door richtlijnen aan te bieden aan ontwikkelaars over hoe grootschalige benchmarkingsexperimenten van computationele methoden kunnen worden uitgevoerd (Hoofdstuk~\ref{chap:guidelines}).
